Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-26 src/tex/conclusion.tex
update refs/concl/macros

% spin dist
Section \ref{sec:spin_dist} focused on inferences of the spin distributions of black holes, observing evidence of spin mis-alignment, spin anti-alignment, and suppressed support 
for exactly aligned systems. These point towards a significant contribution of the population being formed through dynamical formation processes, agreeing with 
conclusions drawn about the mass distribution inference of section \ref{sec:mass_dist}. While field formation is expected to produce systems with preferentially 
aligned spins due to tidal interactions, but observational evidence suggests that tides may not be able to re-align spins in all systems as some 
isolated population models assume. Additionally because of uncertain knowledge of supernovae kicks, isolated formation can produce systems with negative but small effective spins. 
We report an effective spin distribution that is not symmetric about zero, disfavoring a scenarior in wihch all BBHs are formed dynamically. Following the rules in \citet{Fishbach_2022}, 
we place conservative upper bounds on the fraction of hierarhical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$. We find with 
the \textsc{MSpline} model that $f_\mathrm{HM} \leq XX$ and $f_\mathrm{dyn} \leq XX$ at 90\% credibility.

>>>>

% spin dist
Section \ref{sec:spin_dist} focused on inferences of the spin distributions of black holes, observing evidence of spin mis-alignment, spin anti-alignment, and suppressed support 
for exactly aligned systems. These point towards a significant contribution of the population being formed through dynamical formation processes, agreeing with 
conclusions drawn about the mass distribution inference of section \ref{sec:mass_dist}. While field formation is expected to produce systems with preferentially 
aligned spins due to tidal interactions, but observational evidence suggests that tides may not be able to re-align spins in all systems as some 
isolated population models assume. Additionally because of uncertain knowledge of supernovae kicks, isolated formation can produce systems with negative but small effective spins. 
We report an effective spin distribution that is not symmetric about zero, disfavoring a scenarior in wihch all BBHs are formed dynamically. Following the rules in \citet{Fishbach_2022}, 
we place conservative upper bounds on the fraction of hierarhical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$ with 
the \textsc{MSpline} $\chi_\mathrm{eff}$ model constraining $f_\mathrm{HM} < $\result{$\macros[ChiEffective][chieff][frac_hm][10th percentile]$} 
and $f_\mathrm{dyn} < $\result{$\macros[ChiEffective][chieff][frac_dyn][10th percentile]$} at 90\% credibility.
